\documentclass[10pt]{article}

\title{Characterizing tandem fin wake interaction using lateral line inspired sensors}
\author{MIDN 2/C Cameron Smith\thanks{Department of Weapons, Robotics, and Control Engineering at the United States Naval Academy. Address for correspondence \emph{m226072@usna.edu}}}
\date{\today}
\usepackage[separate-uncertainty=true]{siunitx}
\usepackage{amsmath,amsfonts,amssymb}
%\DeclareSIUnit{\sec}{s}
%\DeclareSIUnit{\centimeter}{cm}
%\DeclareSIUnit{\meter}{m}
%\DeclareSIUnit{\kilogram}{kg}
\usepackage[plain]{fancyref}
\usepackage{listings}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[round,authoryear]{natbib}
\bibliographystyle{apalike}
\begin{document}
\maketitle
\begin{abstract}

    Fish have demonstrated extreme agility underwater, a desirable trait for unmanned underwater vehicles (UUVs). Much of a fish's maneuverability can be attributed to the complex interactions between the wakes made by its multiple control surfaces. One such interaction of great interest to this project is the interference between vortex wakes produced by the dorsal and caudal fins. The degree of thrust increase from these interactions is influenced by the phase difference between the flapping fins. To incorporate this type of movement in bio-inspired vehicles, it is desirable to develop a feedback architecture that detects the degree of wake interaction.
    %This research project will work toward the development of a feedback control loop for two, two-dimensional tandem fins. In previous work, pressure sensor arrays have accurately characterized single vortex streets. This project will study their response to double vortex wakes to develop a system that provides real-time feedback on tandem foil wake interactions. The pressure sensor array for this project is inspired by the lateral line in fish, an organ that detects flow oscillations.
    
    The goal of this project is to engineer a two dimensional tandem fin system capable of coordinating flapping foils to improve thrust generation using an array of pressure sensors inspired by the fish lateral line system. This research draws inspiration from the flow control properties of dorsal and caudal fin coordination in bony fish and their ability to sense important fluid properties with their lateral line. It also applies observations and techniques used by previous teams to study single vortex wakes using artificial lateral lines. Several experimental trials will be performed in USNA's Large Re-Circulating Water Tunnel to collect wake pressure data downstream from two tandem fins flapping at multiple phase differences. Based on these trials, features of the data will be found that vary according to phase difference. Relationships between these features and the known phase difference will be found using nonlinear methods, enabling a system to map observed wake features to upstream phase difference.
    
    Progress in this field will be beneficial, as control systems capable of calculating tandem foil phase difference will directly relate it to foil thrust production. This will enable more robust and agile underwater locomotion, which contributes to the ability to perform dexterous tasks in difficult environments, such as closely studying coral reefs, maneuvering through subsea obstacles, and UUV schooling.
    
\end{abstract}
% anatomy wise - dorsal fin on a whale is at 90 deg to the 
% tail flukes.. previous usna work dealt with humpback whale
% pectoral fin which does not have an upstream thing 
{\scriptsize Keywords: flapping foil, sensing, biomechanics, hydrodynamics, maneuvering, lateral line, tandem foils}
\tableofcontents
\input{Components/Background} 
\input{Components/Previouswork} 
\input{Components/Goalsandobj}
\input{Components/Methods}
\input{Components/Analysis}
\input{Components/Implications}
\input{Components/Riskmanagement}
\input{Components/Conclusion}

\bibliography{trident.bib}
%\input{Components/Appendix A}
\end{document}

% DE: things to consider; sensing forces, sensing vibration,
% sensing if flow is attached, sensing lift/drag on fin, 
% sensing "luffing"... we've jumped straight to something about
% vorticity and circulation from an upstream body without
% explaining why; also look up stall sensing for wings, 
% GI taylor vorticity video where he makes little devices 
% track vorticity...